{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-11 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

    \section{Hoffman error bound in linear feasibility problem}

\chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
    This chapter is the draft for an upcoming paper. 
    The writing style will change to fit this purpose better. 
    \par
    There are several notable enhancements of the FISTA for function that are not strongly convex. 
    Monotone variants are proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018}. 
    Chambolle proposed the Backtracking strategy \cite{calatroni_backtracking_2019}.
    Restart is a technique can be found in Necoara et al. \cite{necoara_linear_2019}, \cite{alamo_restart_2019} and Aujol et al. \cite{aujol_parameter-free_2024}.

@@

        This section introduces the full scope of the theories in our analysis. 

@@

            The following assumption is strictly stronger than \ref{ass:sum-of-wcnvx}. 

@@

                Let $F = f + g$ where $f:\RR^n\rightarrow \overline \RR$ is $L$ Lipschitz smooth, $g$ is convex. 
                Suppose that $\argmin_{x \in \RR^n} F(x)\neq \emptyset$.

@@

        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 
        We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 
        The following definition captures several monotone variants of FISTA with line search,  or backtracking strategies.

@@

        In this section, we give convergence results for a unified formulation of monotone accelerated proximal gradient methods with line search or backtracking enhancements. 
        Definition \ref{def:generic-mapg-ls} gives a unified view of several combined heuristics. 
        Theorem \ref{thm:gmapg-ls-convergence} gives a generic description for the convergence rate. 
        Lemma \ref{lemma:gmapg-seq-bnd} specializes the sequence, attains the lowest upper bound. 
        Theorem \ref{thm:gmapg-specialized-cnvg} gives a concrete $\mathcal O(1/k^2)$ upper bound for the optimality gap and normed gradient mapping on the last iteration. 
        ``MAPG'' stands for monotone accelerated gradient. 
        We refer to ``Generic Monotone Accelerated Proximal Gradient with line search" as ``GMAPG''. 
        \begin{definition}[GMAPG]\label{def:generic-mapg-ls}\;\\ 

@@

                    & \text{Choose any } x_k: F(x_k) \le \min(F(\tilde x_k), F(x_{k - 1})). 

@@

@@

            Take $(L_k)_{k \ge 0}$ from Definition \ref{def:generic-mapg-ls} so it has $L_k > 0$ for all $k \in \N \cup \{0\}$. 
            The sequence $(\rho_k)_{k \ge 0}$ is defined as 

@@

            Define sequence $(\beta_k)_{k \ge 0}$ such that $\beta_0 = 1$ and for all $k \ge 1$: 

@@

            The iterates $(x_k, v_k, y_k)_{k \ge 1}$ generated by Definition \ref{def:generic-mapg-ls}. 

@@

        \begin{theorem}[generic GMAPG convergence]\; \label{thm:gmapg-ls-convergence}\;\\

@@

            Then, for all $x^+ \in \RR^n, k \ge 1$, the convergence rate of GMAPG (Definition \ref{def:generic-mapg-ls}) is given by: 

@@

            In the proof follows, the follow facts will be used. 
            We list them in advance, and they will be labeled during the proof. 

@@

                \item Lemma \ref{lemma:apg-iterates}. 
                \item The sequence $(\alpha_k)_{k \ge 1}$ has for all $k \ge 1$, $1 - \alpha_k = \alpha_k^2\alpha_{k - 1}^2\rho_{k - 1}$, $\alpha_k \in (0, 1)$ from Definition \ref{def:alpha-beta-rho-seq}. 
                \item $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$ from Assumption \ref{ass:standard-fista}. 
                \item $F(x_k) \le F(\tilde x_k)$ which is true by definition of GMAPG (Definition \ref{def:generic-mapg-ls}). 

@@

                &\underset{\text{(i)}}{=}

@@

                + \frac{L_k\alpha_k^2}{2}\Vert(x^+ - v_{k - 1})\Vert^2
                &\hspace{-0.3em}\underset{\text{(iii)}}{\le} 

@@

                &\hspace{-0.3em}\underset{\text{(iv)}}{\le} 

@@

@@

        \begin{theorem}[generic GMAPG gradient mapping convergence]\;\label{thm:gmapg-generic-gm-cnvg}\\

@@

            % Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}).
            Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}), and take the momentum sequences $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}. 

@@

                \item The sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $L_0 \ge L$ or, equivalently a successful line search satisfying \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$};

@@

            \begin{align}\label{ineq:gmapg-generic-gm-cnvg-prt1}

@@

            \begin{align}\label{ineq:gmapg-generic-gm-cnvg-prt2}

@@

            \eqref{ineq:gmapg-generic-gm-cnvg-prt2} is direct because $x_0 = T_{1/L_0, f, g}(x_{-1})$ and \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$} is assumed in the statement hypothesis, using \ref{lemma:fitsa-pg-ineq} with $x = x_{-1}, z = x_{-1}$, using  gradient mapping as defined in Definition \ref{def:gm-for-ch2} it has 

@@

                &= (F(x_{-1}) - F(\bar x)) - \frac{L_0}{2}\Vert L_0^{-1}\mathcal G_{1/L_0}(x_{-1})\Vert^2. 
            We label the following results prior to their proofs for a sleeker exposition for the proof of \eqref{eqn:emp:result-item-2}. 

@@

                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} (y_k)\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
                \item[(b)] We have $(a_k)_{k \ge 1}$ satisfying $\forall k \ge 1$ that $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis. We assumed $\alpha_0 = 0, \beta_0 = 1$, $x^+$ is a minimizer of $F$. Then using these it has for all $k \ge 0$ it has $\frac{\alpha_k}{\sqrt{\beta_k L_0}}\Vert x^+ - v_k\Vert \le \Vert x^+ - v_0\Vert$. 

@@

            Using the above intermediate results, the convergence in \eqref{ineq:gmapg-generic-gm-cnvg-prt1} can be derived. 

@@

            From the definition of GMAPG it has 

@@

            Using the above, and definition of GMAPG, it yields 

@@

                = \alpha^{-1}_k(\tilde x_k - y_k) = \alpha_k^{-1}(T_{L_k} y_k - y_k)

@@

            For all $k \ge 1$, we consider the convergence claim and use the assumption that $x^+$ is a minimizer of $F$ so, it has from Theorem \ref{thm:gmapg-ls-convergence} that 

@@

        \begin{lemma}[specialized GMAPG momentum sequence]\;\label{lemma:gmapg-seq-bnd}\\

@@

            For all $k \ge 1$ let $\widehat L_k = \max_{i = 0, 1, \ldots, k} L_i$ then 

@@

            This simplifies the convergence claim back in Theorem \ref{thm:gmapg-ls-convergence}. 
            The above inequality would work the same if we set: 

@@

        \begin{theorem}[specialized GMAPG convergence rate]\label{thm:gmapg-specialized-cnvg}

@@

            Let the sequences $(x_k, v_k, v_k)_{k \ge 0}$ and $(L_k)_{k \ge 0}$ satisfy GMAPG in Definition \ref{def:generic-mapg-ls} and, assume that the GMAPG is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 

@@

            To see (i), use Lemma \ref{lemma:gmapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ suit. 
            To see (ii), the convergence claim from \ref{thm:gmapg-generic-gm-cnvg} simplifies with $\widehat L_k \ge L_0$ and, it has 

@@

    \section{Algorithmic description of GMAPG}
        There are several components to the GMAPG algorithm. 
        This section will introduce various type of implementations that can be fitted into GMAPG in Definition \ref{def:generic-mapg-ls}. 

@@

                \item $x, v$ are the $x_k, v_k$ iterates in Definition \ref{def:generic-mapg-ls}. 
                \item $\alpha$ are the current $\alpha_k$ in Definition \ref{def:generic-mapg-ls}. 

@@

        \subsection{Monotone routines}
            % BECK'S MONO ------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function BeckMono Inputs: }
                        \begin{tabular}{|ll}
                            $f: \RR^n \rightarrow \RR$ & Convex Smooth\\
                            $g: \RR^n \rightarrow \overline \RR$ & Convex\\
                            $\tilde x \in \RR^n$ & Vector\\
                            $x \in \RR^n$ & Vector\\
                            $\rho$ & Number $\rho \in (0, 1)$ Number\\
                            $G \in \RR$ & Number 
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $x^+ = \argmin \{(f + g)(z): z \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\textbf{Return: } $x^+, \eta, G$}
                    \caption{Beck's monotone routine}\label{alg:beck-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            Algorithm \ref{alg:beck-mono} is a subroutine for asserting monotone condition on function value. 
            The parameter $G$ has no actual usage besides making it compatible with Algorithm \ref{alg:nes-mono} in the context of Algorithm \ref{alg:gmapg}. 
            The input $\tilde x$ is the candidate iterate produced by FISTA without monotone constraints and $x$ is the previous iterates $x_{k - 1}$ in the inner loop. 
            % NES'S MONO -------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function NesMono Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n\rightarrow \RR$ & Lipschitz Smooth \\ 
                            $g: \RR^n \rightarrow \overline \RR$ & Weakly Convex \\ 
                            $\tilde x \in \RR^n$ & Vector \\ 
                            $x \in \RR^n$ & Vector \\
                            $\eta \in \RR$ & Number $\eta > 0$\\
                            $G \in \RR$  & Number
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $\hat y := \argmin\{(f + g)(z), x \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\noindent
                        $x^+ := T_{1/\eta}(\hat y)$. 
                    }
                    \FOR {i = 1, 2, \ldots, 53}
                        \IF{$(f + g)(x^+) - (f + g)(\hat y) \le -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
                            \STATE{\textbf{Break}}
                        \ENDIF
                        \STATE{$\eta := 2\eta$. }
                            \STATE{$x^+ := T_{1/\eta}(\hat y)$.}
                    \ENDFOR
                    \STATE{$G := \eta (x^+ - \hat y).$}
                    \STATE{\textbf{return: } $x^+, \eta, G$ }
                    \caption{Nesterov's monotone routine}\label{alg:nes-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            The above Algorithm \ref{alg:nes-mono} implements and adapts Nesterov's monotone scheme from Nesterov \cite[2.2.32]{nesterov_lectures_2018} for GMAPG. 
            In addition to Algorithm \ref{alg:beck-mono}, $\eta$ is a new input parameter and $G$ has a significance role. 
            $\eta$ is a stepsize parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
            $G$ is the norm of the gradient mapping updated at at $\hat y$ which will be returned to the inner loop to verify exit conditions.

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function GMAPG Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}
                    \IF{$G_0 \le \epsilon$}
                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}
                    \ENDIF
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= \Vert \sqrt L_k(\tilde x_k - y_k)\Vert $}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
            The first iterates $x_0$ is produced by a step of proximal gradient descent through Algorithm \ref{alg:armijo-ls} so, it has $x_0 = v_0 = T_{1/L_0}(x_{-1})$, and consequently all results from Theorem \ref{thm:gmapg-specialized-cnvg} apply. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.

    \section{Examples of GMAPG in the literature}

@@

            We now demonstrate that Algorithm \ref{alg:mfista-armijo} is a special case of Definition \ref{def:generic-mapg-ls}.
            Let's consider $y_{k + 1}$ produced the GMAPG. 

@@

        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\
            The following is (2.2.32) in Nesterov's book, phrased in our GMAPG framework. 
            \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
            \STATE{\textbf{Input: } }
            \end{algorithmic}\caption{Nesterov's monotone scheme with generic line search}

@@

        The following definition is a set of necessary conditions GMAPG with Nesterov's monotone subroutine. 
        Our goal in this section is to show that Nesterov's implementations of monotone accelerated gradient method has convergence results under Assumption \ref{ass:sum-of-wcnvx}.

@@

@@

        In this section, we show that restarting GMAPG with a well suited conditions yields fast linear global convergence. 
        We adapt and improve prior theories from Alamo \cite{alamo_restart_2019} for our GMAPG method. 

>>>>

    \section{Hoffman error bound of linear feasibility problem}
    \section{Quadratic growth of linear feasibility problem}

\chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
    %% SYMBOL SETS FOR THIS CHAPTER ONLY 
    \newcommand{\XXAPG}{AMAPG}

    This chapter is the draft for an upcoming paper. 
    The writing style will change to fit this purpose better. 
    It will be very terse. 
    \par
    There are several notable enhancements of the FISTA for function that are not necessarily strongly convex. 
    Monotone variants are proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018}. 
    Chambolle proposed the Backtracking strategy \cite{calatroni_backtracking_2019}.
    Restart is a technique can be found in Necoara et al. \cite{necoara_linear_2019}, \cite{alamo_restart_2019} and Aujol et al. \cite{aujol_parameter-free_2024}.

@@

@@

@@

                Let $F = f + g$ where $f:\RR^n\rightarrow \overline \RR$ is $L$ Lipschitz smooth, $g$ is convex and, $\argmin_{x \in \RR^n} F(x)\neq \emptyset$.

@@

        This section gives convergence results under a unified perspective of accelerated proximal gradient methods with line search, backtracking, and monotone enhancements. 
        Definition \ref{def:xxapg} unifies several combined heuristics. 
        Theorem \ref{thm:xxapg-fxn-cnvg} provides a generic convergence rate for all momentum sequence satisfying Definition \ref{def:alpha-beta-rho-seq}. 
        A specialized sequence is stated in Lemma \ref{lemma:xxapg-seq-bnd} which attains the lowest upper bound on the convergence rate. 
        Theorem \ref{thm:xxapg-specialized-cnvg} proves the $\mathcal O(1/k^2)$ for optimality gap and, the norm of gradient mapping on the last iterate. 

@@

        ``Abstract Monotone Accelerated Proximal Gradient with line search" is ``\XXAPG{}''. 
        \begin{definition}[\XXAPG{}]\label{def:xxapg}\;\\ 

@@

                    & \text{Choose any } x_k: F(x_k) \le F(\tilde x_k). 

@@

            Having $F(x_k) \le F(\tilde x_k)$ doesn't necessarily mean $F(x_k) \le F(x_{k - 1})$. 

@@

            Let $(L_k)_{k \ge 0}$ satisfy $L_k > 0$ for all $k \in \N \cup \{0\}$. 
            Define the sequence $(\rho_k)_{k \ge 0}$ by:

@@

            Define the sequence $(\beta_k)_{k \ge 0}$, let $\beta_0 = 1$ and, for all $k \ge 1$ it's defined by: 

@@

            The iterates $(x_k, v_k, y_k)_{k \ge 1}$ generated by Definition \ref{def:xxapg}. 

@@

        \begin{theorem}[generic \XXAPG{} convergence]\; \label{thm:xxapg-fxn-cnvg}\;\\

@@

            Then, for all $x^+ \in \RR^n, k \ge 1$, the convergence rate of \XXAPG{} (Definition \ref{def:xxapg}) is given by: 

@@

            In the proof that follows, we list some facts in advance before their proofs which come later. 

@@

                \item[(a)] Lemma \ref{lemma:apg-iterates}. 
                \item[(b)] The sequence $(\alpha_k)_{k \ge 1}$ has for all $k \ge 1$, $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$, $\alpha_k \in (0, 1)$ from Definition \ref{def:alpha-beta-rho-seq}. 
                \item[(c)] $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$ from Assumption \ref{ass:standard-fista}. 
                \item[(c)] $F(x_k) \le F(\tilde x_k)$ which is true by definition of \XXAPG{} (Definition \ref{def:xxapg}). 

@@

@@

                &\underset{\text{(c)}}{\le} 

@@

@@

                &\underset{\text{(b)}}{=} 

@@

        \begin{theorem}[generic \XXAPG{} gradient mapping convergence]\;\label{thm:xxapg-gm-cnvg}\\

@@

            % Let the sequences $(x_k, y_k, v_k)$ satisfy \XXAPG{} (Definition \ref{def:xxapg}).
            Let the sequences $(x_k, y_k, v_k)$ satisfy \XXAPG{} (Definition \ref{def:xxapg}), and take the momentum sequences $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}. 

@@

                \item The sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, \XXAPG{} is initialized with $L_0 \ge L$ or, equivalently a successful line search satisfying \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$};

@@

            \begin{align}\label{ineq:xxapg-gm-cnvg-prt1}

@@

            \begin{align}\label{ineq:xxapg-gm-cnvg-prt2}

@@

            \eqref{ineq:xxapg-gm-cnvg-prt2} is direct because $x_0 = T_{1/L_0, f, g}(x_{-1})$ and \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$} is assumed in the statement hypothesis, using Lemma \ref{lemma:fitsa-pg-ineq} with $x = x_{-1}, z = x_{-1}$, by Definition \ref{def:gm-for-ch2} it has 

@@

                &= F(x_{-1}) - F(x_0) - \frac{L_0}{2}\Vert L_0^{-1}\mathcal G_{1/L_0}(x_{-1})\Vert^2. 
            We label the following results prior to their proofs which will come later for a sleeker exposition for the proof of \eqref{eqn:emp:result-item-2}. 

@@

                \item[(a)] From Definition \ref{def:xxapg}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} (y_k)\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
                \item[(b)] We have $(a_k)_{k \ge 1}$ satisfying $\forall k \ge 1$ that $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis. We assumed $\alpha_0 = 0, \beta_0 = 1$, $x^+$ is a minimizer of $F$ and, a successful line search in item (i). Then using these it has for all $k \ge 0$ it has $\frac{\alpha_k}{\sqrt{\beta_k L_0}}\Vert x^+ - v_k\Vert \le \Vert x^+ - v_0\Vert$. 

@@

            Using the above intermediate results, the convergence in \eqref{ineq:xxapg-gm-cnvg-prt1} can be derived. 

@@

            From the Definition \ref{def:xxapg} it has 

@@

            Current iterates $v_k$ is updated via $x_{k-1}, \tilde x_k$ so consider:

@@

                = \alpha^{-1}_k(\tilde x_k - y_k) = \alpha_k^{-1}(T_{1/L_k} y_k - y_k)

@@

            For all $k \ge 1$, we consider the convergence claim and use the assumption that $x^+$ is a minimizer of $F$ so, it has from Theorem \ref{thm:xxapg-fxn-cnvg} that 

@@

        \begin{lemma}[specialized \XXAPG{} momentum sequence]\;\label{lemma:xxapg-seq-bnd}\\

@@

            For all $k \ge 1$ let  
            Then, 

@@

            This simplifies the convergence claim back in Theorem \ref{thm:xxapg-fxn-cnvg}. 

@@

        \begin{theorem}[specialized \XXAPG{} convergence rate]\label{thm:xxapg-specialized-cnvg}

@@

            Let the sequences $(x_k, v_k, v_k)_{k \ge 0}$ and $(L_k)_{k \ge 0}$ satisfy \XXAPG{} in Definition \ref{def:xxapg} and, assume that the \XXAPG{} is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 

@@

            To see (i), use Lemma \ref{lemma:xxapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:xxapg-fxn-cnvg} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ suit. 
            To see (ii), the convergence claim from \ref{thm:xxapg-gm-cnvg} simplifies with $\widehat L_k \ge L_0$ and, it has 

@@

    \section{Algorithmic description of \XXAPG{}}
        There are several components to the \XXAPG{} algorithm. 
        This section will introduce various type of implementations that can be fitted into \XXAPG{} in Definition \ref{def:xxapg}. 

@@

                \item $x, v$ are the $x_k, v_k$ iterates in Definition \ref{def:xxapg}. 
                \item $\alpha$ are the current $\alpha_k$ in Definition \ref{def:xxapg}. 

@@

        \subsection{Monotone routines}
            % BECK'S MONO ------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function BeckMono Inputs: }
                        \begin{tabular}{|ll}
                            $f: \RR^n \rightarrow \RR$ & Convex Smooth\\
                            $g: \RR^n \rightarrow \overline \RR$ & Convex\\
                            $\tilde x \in \RR^n$ & Vector\\
                            $x \in \RR^n$ & Vector\\
                            $\rho$ & Number $\rho \in (0, 1)$ Number\\
                            $G \in \RR$ & Number 
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $x^+ = \argmin \{(f + g)(z): z \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\textbf{Return: } $x^+, \eta, G$}
                    \caption{Beck's monotone routine}\label{alg:beck-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            Algorithm \ref{alg:beck-mono} is a subroutine for asserting monotone condition on function value. 
            The parameter $G$ has no actual usage besides making it compatible with Algorithm \ref{alg:nes-mono} in the context of Algorithm \ref{alg:xxapg}. 
            The input $\tilde x$ is the candidate iterate produced by FISTA without monotone constraints and $x$ is the previous iterates $x_{k - 1}$ in the inner loop. 
            % NES'S MONO -------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function NesMono Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n\rightarrow \RR$ & Lipschitz Smooth \\ 
                            $g: \RR^n \rightarrow \overline \RR$ & Weakly Convex \\ 
                            $\tilde x \in \RR^n$ & Vector \\ 
                            $x \in \RR^n$ & Vector \\
                            $\eta \in \RR$ & Number $\eta > 0$\\
                            $G \in \RR$  & Number
                        \end{tabular}\vspace{0.5em}
                    }
                    \STATE{\noindent
                        $\hat y := \argmin\{(f + g)(z), x \in \{\tilde x, x\}\}$. 
                    }
                    \STATE{\noindent
                        $x^+ := T_{1/\eta}(\hat y)$. 
                    }
                    \FOR {i = 1, 2, \ldots, 53}
                        \IF{$(f + g)(x^+) - (f + g)(\hat y) \le -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
                            \STATE{\textbf{Break}}
                        \ENDIF
                        \STATE{$\eta := 2\eta$. }
                            \STATE{$x^+ := T_{1/\eta}(\hat y)$.}
                    \ENDFOR
                    \STATE{$G := \eta (x^+ - \hat y).$}
                    \STATE{\textbf{return: } $x^+, \eta, G$ }
                    \caption{Nesterov's monotone routine}\label{alg:nes-mono}
                \end{algorithmic}
            \end{algorithm}
            \par
            The above Algorithm \ref{alg:nes-mono} implements and adapts Nesterov's monotone scheme from Nesterov \cite[2.2.32]{nesterov_lectures_2018} for \XXAPG{}. 
            In addition to Algorithm \ref{alg:beck-mono}, $\eta$ is a new input parameter and $G$ has a significance role. 
            $\eta$ is a stepsize parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
            $G$ is the norm of the gradient mapping updated at $\hat y$ which will be returned to the inner loop to verify exit conditions.

        \subsection{\XXAPG{} main algorithm}
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function \XXAPG{} Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}
                    \IF{$G_0 \le \epsilon$}
                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}\label{alg:xxapg-exit1}
                    \ENDIF
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= \Vert \sqrt L_k(\tilde x_k - y_k)\Vert $}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}\label{alg:xxapg-exit2}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                \caption{\XXAPG{} with Chambolle's backtracking}\label{alg:xxapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:xxapg} is an implementation of \XXAPG{} in Definition \ref{alg:xxapg}. 
            The first iterates $x_0$ is produced by a step of proximal gradient descent through Algorithm \ref{alg:armijo-ls} so, it has $x_0 = v_0 = T_{1/L_0}(x_{-1})$, and consequently all results from Theorem \ref{thm:xxapg-specialized-cnvg} apply. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$. 
            \begin{observation}[\XXAPG{} exit conditions]
                Algorithm \ref{alg:xxapg} exits and returns its results on line \ref{alg:xxapg-exit1}, or at line \ref{alg:xxapg-exit2}. 
                If exited, then at least one of the conditions are true. 
            \end{observation}

    \section{Examples of \XXAPG{} in the literature}

@@

            We now demonstrate that Algorithm \ref{alg:mfista-armijo} is a special case of Definition \ref{def:xxapg}.
            Let's consider $y_{k + 1}$ produced the \XXAPG{}. 

@@

        % \begin{example}[Nesterov's monotone scheme with generic line search]\;\\
        %     The following is (2.2.32) in Nesterov's book, phrased in our \XXAPG{} framework. 
        %     \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
        %     \begin{algorithmic}[1]
        %     \STATE{\textbf{Input: } }
        %     \end{algorithmic}\caption{Nesterov's monotone scheme with generic line search}
        %     \end{algorithm}
        % \end{example}

@@

        Under Assumption \ref{ass:sum-of-wcnvx}, Theorem \ref{thm:nes-mono-wcnvx-convergence} shows the Nesterov's monotone algorithm in Definition \ref{def:nes-monotone-scheme} eventually terminate. 

@@

        See Nesterov's book \cite{nesterov_lectures_2018} for more details.

@@

        We adapted and improved prior theories on FISTA restart with global linear convergence from Alamo \cite{alamo_restart_2019} for our \XXAPG{} method. 
